Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-04-12 sections/3algebras.tex
Some work in section 4.
Small correction in section 3.5.

@@

\begin{proof}
    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk (\mathsf{D}_n^*) \xrightarrow{\ \ \simeq \ \ } \mathbb{E}_n.
    \end{equation}
    %
    But this is just the classical fact, that the little $n$-disks operad and the little $n$-cubes operad are equivalent, in disguise.
\end{proof}

@@

\begin{remark}[{\cite[prop.3.16]{francis2013}, \cite[ex.5.5.4.16]{lurie_ha}}]
    In the case of Euclidean spaces like $\mathbb{R}^n$, essentially because of translation invariance, a special thing happens when we restrict away from the origin. That is, we know that given a locally constant factorization algebra $F$ on $\mathbb{R}^n$ we can restrict it to any open subset like, for example, $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ to get another locally constant factorization algebra $F|_{S^{n-1} \times \mathbb{R}}$. By \Cref{prop:exp_of_products_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra. If we pushforward to $\mathbb{R}$, by the discussion at \Cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by \footnote{We again refer the reader to \Cref{rem:fh_is_pushingforward} for a reason why this notation is good.}
    %
    \begin{equation}
        \int_{S^{n-1}} F.
    \end{equation}
    %
    What \cite[prop.3.16]{francis2013} shows is then:

>>>>

\begin{remark}
    One perspective on this result, provided by \cite[thm.2.43]{aft_fhstrat}, is that the theory of locally constant factorization algebras captures as much information as (generalized) homology theory in the sense of \cite[def.2.37]{aft_fhstrat}.
\end{remark}

@@

\begin{proof}
    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is a weak equivalence of $\infty$-operads between $\disk (\mathsf{D}_n^*)$ and $\mathbb{E}_n$, i.e.
    %
    \begin{equation}
        \alg{\disk (\mathsf{D}_n^*)} \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n}.
    \end{equation}
    %
    But this is just the fact that the $\disk_{/M}$ $\infty$-operad gives rise to $E_n$-algebras from \cref{prop:framed_ndisk=En}.
\end{proof}

@@

\begin{remark}[{\cite[prop.3.16]{francis2013}, \cite[ex.5.5.4.16]{lurie_ha}}]
    In the case of Euclidean spaces like $\mathbb{R}^n$, essentially because of translation invariance, a special thing happens when we restrict away from the origin. That is, we know that given a locally constant factorization algebra $F$ on $\mathbb{R}^n$ we can restrict it to any open subset like, for example, $\mathbb{R}^n \setminus \{ 0 \} \cong S^{n-1} \times \mathbb{R}$ to get another locally constant factorization algebra $F|_{S^{n-1} \times \mathbb{R}}$. By \Cref{prop:exp_of_products_lc} we know that $F|_{S^{n-1} \times \mathbb{R}} \in \lcfa_{\mathbb{R}} (\lcfa_{S^{n-1}} (\catC))$, so that in particular it is an $\mathbb{E}_1$-algebra. If we pushforward to $\mathbb{R}$, by the discussion at \Cref{rem:fh_is_pushingforward} we could denote the resulting $\mathbb{E}_1$-algebra by
    %
    \begin{equation}
        \int_{S^{n-1}} F.
    \end{equation}
    %
    What \cite[prop.3.16]{francis2013} shows is then:
